Formalizing Stack Safety as a Security Property

### 2021-07-07 submission3/main.tex
Machine model

\bcp{I am having trouble deciding what this section should be called.
  Probably this means I don't really understand its purpose...}
\sna{Propose merging it with next section like so.}

@@

Some calling convention choices, such as callee-save registers and argument
passing on the stack, require enhancements to our base properties. We present
an enhancement that supports argument passing. Other plausible enhancements
include:

@@

Runtime code generation would be much more challenging to support, as
it requires dynamic code annotations. Parallelism would require
fundamental changes to the system model. So, we consider these features
fully out of scope.

>>>>

\bcp{I am having trouble deciding what this section should be called.
  Probably this means I don't really understand its purpose...}
\sna{Propose merging it with next section like so.}
\leo{Machine, Enforcement, and Threat Model?}

@@

Some calling convention choices, such as callee-save registers and argument
passing on the stack, require natural enhancements to our base properties. We
present such enhancements in Section~\ref{sec:ext}, after we formalize the
essence of stack safety. Other plausible enhancements
include:

@@

Runtime code generation would be much more challenging to support, as
it requires dynamic code annotations. Parallelism would require
fundamental changes to the system model. So, we consider these features
fully out of scope.\leo{Shouldn't coroutines be mentioned here?}
